Exploratory Plots

### 2020-06-30 exploratory/2020/README.Rmd
Put boxplot behind hline for mcc plot

# Fitting datasets to a reference database vs _de novo_ clustering
```{r functions}
relevel_method <- function(df) {
  df %>%
    mutate(method = fct_relevel(method, c("open", "closed", "de_novo")))
}
plot_box_mcc <- function(df) {
  df %>%
    group_by(dataset, method) %>%
    ggplot(aes(x = method, y = mcc, color = dataset)) +
    geom_boxplot(alpha = 0.5) +
    scale_color_manual(values = dataset_colors) +
    ylim(0.5, 1) +
    #facet_wrap("ref") +
    facet_grid(dataset ~ ref) +
    theme(legend.position = "None",
          axis.title.x = element_blank())
}
plot_box_time <- function(df) {
  df %>%
    group_by(dataset, method) %>%
    ggplot(aes(x = method, y = s, color = dataset)) +
    geom_boxplot() +
    scale_color_manual(values = dataset_colors) +
    facet_wrap("ref") +
    ylim(0,2100) +
    labs(y = 'seconds') +
    theme(axis.title.x = element_blank())
}
```

### Performance as measured by MCC
```{r fit_db_sensspec}
sensspec_fit <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/sensspec.tsv')) 
sensspec_clust <- read_tsv(here('subworkflows/1_prep_samples/results/sensspec.tsv')) %>% 
  select(-ref) %>% 
  group_by(dataset) %>% 
  summarize(mean_mcc = mean(mcc))
#sensspec <- bind_rows(sensspec_fit, sensspec_clust)

sensspec_fit %>% 
  plot_box_mcc() +
  geom_hline(aes(yintercept = mean_mcc), sensspec_clust) +
  labs(caption = "The black line represents the *de novo* clustering mcc sccore.") +
  theme(plot.caption = element_markdown())
```

>>>>

# Fitting datasets to a reference database vs _de novo_ clustering
```{r functions}
relevel_method <- function(df) {
  df %>%
    mutate(method = fct_relevel(method, c("open", "closed", "de_novo")))
}

plot_box_time <- function(df) {
  df %>%
    group_by(dataset, method) %>%
    ggplot(aes(x = method, y = s, color = dataset)) +
    geom_boxplot() +
    scale_color_manual(values = dataset_colors) +
    facet_wrap("ref") +
    ylim(0,2100) +
    labs(y = 'seconds') +
    theme(axis.title.x = element_blank())
}
```

### Performance as measured by MCC
```{r fit_db_sensspec}
sensspec_fit <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/sensspec.tsv')) 
sensspec_clust <- read_tsv(here('subworkflows/1_prep_samples/results/sensspec.tsv')) %>% 
  select(-ref) %>% 
  group_by(dataset) %>% 
  summarize(mean_mcc = mean(mcc))
#sensspec <- bind_rows(sensspec_fit, sensspec_clust)
sensspec_fit %>%
  group_by(dataset, method) %>%
  ggplot(aes(x = method, y = mcc, color = dataset)) +
  geom_hline(aes(yintercept = mean_mcc), sensspec_clust) +
  geom_boxplot(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  ylim(0.5, 1) +
  facet_grid(dataset ~ ref) +
  labs(caption = "The black line represents the *de novo* clustering mcc sccore.") +
  theme(legend.position = "None",
        axis.title.x = element_blank(),
        plot.caption = element_markdown())
```
